On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-15 manuscripts/PNAS/chazthm_pnas.tex
eqn fix more SR results

@@

We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from the hypergraph $\mathcal{H}$. Letting $\mathbf{M}_J$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define: 
%\begin{align*} 
%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
%\end{align*} 
%
%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$. Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$. For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
%\end{align*} 
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \alpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
%\end{align*} 
\begin{align}\label{Ldef}
L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \inf \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
\end{align} 
%
where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$. Note that if $\mathcal{H}$ covers $[m]$ then $L_2 \geq L_{2\mathcal{H}}$.

A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$. 
%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent. The following is a precise statement of our main result.

@@

We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: 
To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$. When $\bar m = m$, the theorem implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: 
\begin{align}\label{epsdel}
\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
\end{align}

>>>>

\renewcommand{\eqref}[1]{\textnormal{[\ref{#1}]}}

@@

We generalize the  lower bound to a domain-restricted \emph{union of subspaces} model \cite{vidal2005generalized} derived from the hypergraph $\mathcal{H}$. Letting $\mathbf{M}_J$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $J$ (with $\mathbf{M}_\emptyset := \mathbf{0}$), we define: 
%\begin{align*} 
%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
%\end{align*} 
%
%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$. Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$. For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
%\end{align*} 
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \alpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
%\end{align*} 
\begin{align}\label{Ldef}
L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \inf \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
\end{align} 
%
where we write $L_{k}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that $1 - \sqrt{k} L_k(\mathbf{M})$ is known as the asymmetric lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$. Note that if $\mathcal{H}$ covers $[m]$ t(i.e., $\cup \mathcal{H} = [m]$), then $L_2 \geq L_{2\mathcal{H}}$.

A vector $\mathbf{x}$ is said to be \emph{supported} in $S \subseteq [m]$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$. 
%Denote by $\mathbf{x}^J$ the subvector formed from the entries of $\mathbf{x}$ indexed by $J$. 
A set of $k$-sparse vectors is said to be in \emph{general linear position} when any $k$ of them are linearly independent. The following is a precise statement of our main result.  Only the quantity $C_1$ is undefined until later (in Sec.~\ref{DUT}, Eq.~\eqref{Cdef1}).

@@

%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: 
To be clear, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the difference $\bar m - m$, the more columns and coefficients of the original dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ are contained (up to noise) in the appropriately scaled dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$. When $\bar m = m$, the theorem implies that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequality \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: 
\begin{align}\label{epsdel}
\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
\end{align}
